Contextual Identity: Towards Usable Privacy

### 2013-03-06 paper.tex
tiny fix, based on elastic self

The following examples illustrate how users attempt to preserve boundaries
between identities. None of these techniques are failsafe, but they serve as
useful reminders that perfect solutions may not be necessary, especially in the
case where information leaks by casual or accidental inspection.

>>>>

The following examples illustrate how users attempt to preserve boundaries
between identities. None of these techniques are failsafe, but they serve as
useful reminders that perfect solutions may not be necessary or even desirable,
especially in the case where information leaks by casual or accidental
inspection.
